SVG: The Paper

### 2022-04-14 Analysis/index.Rmd
Added a note on path lengths

plts[[1]] + plts[[2]] 
```

>>>>

plts[[1]] + plts[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8"))
```

# Shortest Path Analysis

It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to mimimise overall path length. Here we will compare our model's predicted path length against the empirical paths.
